In the design of embedded and cyber-physical systems, one of the most
important requirements is safety, which can be roughly stated as that
the system will never enter a bad state. Safety verification for such
systems are known to be computationally challenging due to the
complexity resulting from the interactions among heterogenous
components, having mixed (continuous and discrete) dynamics. In this
paper, we focus on the problem of finding invariants for hybrid
systems, which are widely recognized as appropriate for modelling
embedded and cyber-physical systems. An invariant is a property that
is satisfied in every state that the system can reach. Therefore a
common approach for proving a safety property is to find an invariant
that implies the safety property. Invariant computation has been
studied extensively in the context of verification of transition
systems and program analysis (see for
example~\cite{CousotHalbwachs78,DBLP:journals/fmsd/BensalemL99,DBLP:conf/tacas/TiwariRSS01,DBLP:conf/cav/ColonSS03,DBLP:conf/sas/Goubault13}
and the developed techniques have been extended to continuous and
hybrid
systems \cite{DBLP:conf/hybrid/SankaranarayananSM04,jeannet2009apron,DBLP:conf/hybrid/Rodriguez-CarbonellT05,DBLP:conf/cdc/SassiGS14,DBLP:journals/tecs/AllamigeonGSGP16,HybridFluctuat,DBLP:conf/vmcai/SogokonGJP16,DBLP:conf/aplas/DangG11}. Barrier
certificates \cite{prajna2004safety} are closely related to invariants
in the sense that they describe a boundary that the system starting
from a given initial set will never cross to enter a region containing
bad states. Another common approach to safety verification is to
compute or over-approximate the reachable set of the system, and these
reachability computation techniques have been developed for continuous
and hybrid systems.  Many such techniques are based on iterative
approximation of the reachable state on a step-by-step basis, which
can be thought of as a set-based extension of numerical integration. A
major drawback of this approach, inherent to undecidability of general
hybrid systems with non-trivial dynamics, is that such an iterative
procedure may not terminate and thus can only be used for bounded-time
safety verification (except when the over-approximation error
accumulation is not too bad that the safety can be decided). In
contrast, invariants and barrier certificates are based
on conditions that are satisfied at all times. Although solving these
conditions often involves fixed point computation, by exploiting the
structure of the dynamics (such as eigenstructures of linear systems),
one can derive meaningful conditions which can significantly reduce
the number of iterations until convergence.

\input{contribution}

\emph{Related work.} For hybrid systems verification, convex polyhedra~\cite{CousotHalbwachs78,jeannet2009apron}, and their special classes such as
zones~\cite{DBLP:conf/pado/Mine01},
octagons~\cite{DBLP:journals/lisp/Mine06}, zonotopes~\cite{DBLP:conf/hybrid/Girard05,DBLP:conf/eucc/MaigaCRT14} and
tropical polyhedra~\cite{DBLP:conf/sas/AllamigeonGG08} are the most
commonly used set representations. During the analysis which requires
operations under which a set representation is not closed (such as the
union or join operations for convex polyhedra and additionally
intersection for zonotopes) the complexity of generated sets increases
rapidly in order to guarantee a desired error bound. One way to
control this complexity increase, face normal vectors or generators
are fixed, which leads to template convex
polyhedra \cite{Sankaranarayanan+Dang+Ivancic-08-Symbolic,DBLP:conf/aplas/DangG11}. Although
our template complex zonotopes proposed in~\cite{tcz2017} do not
belong to the class of convex polyhedra, they follow the same
spirit of controlling the complexity. Set representations defined by non-linear constraints include
ellipsoids~\cite{Kurzhanski2000201}, polynomial
inequalities\cite{DBLP:conf/sas/BagnaraRZ05} et
equalities~\cite{Rodriguez-Carbonell:2007}, quadratic templates and
piecewise quadratic
templates~\cite{DBLP:conf/esop/AdjeGG10,DBLP:conf/hybrid/RouxJGF12,DBLP:conf/fm/RouxG14,DBLP:conf/hybrid/Adje17},
which are used for computing non-linear invariants. A major problem
that the template based approach faces is finding good templates. As
it will become clear later, using template complex zonotopes and the
augmented version introduced in this paper and exploiting
eigen-structures of linear dynamics which reflect the contraction or
expansion of a set by the dynamics, allows requiring only few of steps
until convergence to an invariant.

The complex zonotopes we proposed in~\cite{adimoolamACC2016} extend
usual zonotopes to the complex domain, and geometrically speaking they
are Minkowski sum of line segments and some ellipsoids. This extension
is very similar in spirit to quadratic
zonotopes~\cite{DBLP:conf/aplas/AdjeGW15} and more generally
polynomial zonotopes~\cite{DBLP:conf/hybrid/Althoff13}. Nevertheless,
while a polynomial zonotope is a set-valued polynomial function
of \emph{intervals}, a complex zonotope is a set-valued function of
unit \emph{circles} in the complex plane. Our idea of coupling
additional linear constraints with zonotopes is inspired by the work
on constrained zonotopes proposed
in~\cite{DBLP:conf/cav/GhorbalGP09,scott2016constrained} for
intersection computation.  But
while~\cite{DBLP:conf/cav/GhorbalGP09,scott2016constrained} compute
the intersection or its overapproximation algorithmically, we instead
derive a simple algebraic expression to overapproximate the
intersection.  This is because we use the algebraic expression to
derive second order conic (convex) constraints for invariant computation.\\

\emph{Organization.}  The rest of the paper is organized as follows.  Firstly, we explain
some of the mathematical notation used in this paper.  Then in
Section~\ref{sec:system}, we describe the model of a discrete-time
affine hybrid system, controlled by sub-parallelotopic switching
conditions and having a bounded additive disturbance input. In
Section~\ref{sec:acz}, we present the set representation of augmented
complex zonotopes and discuss some important operations and relations, in particular intersection with sub-parallelotopic constraints, projection in any direction, linear transformation, Minkowski sum and inclusion checking.  In
Section~\ref{sec:invcomp}, we derive a set of second order conic
constraints to compute an augmented complex zonotopic invariant,
satisfying linear safety constraints and containing an initial set.
Furthermore, we explain how to choose the template.  In
Section~\ref{sec:exp}, we report some experimental results.  The
conclusion and future work are given in Section~\ref{sec:conclusion}.
We annex proofs of some lemmas presented in the paper in an
Appendix.

\emph{Notation.} Some notations, for which we
consider explanation may be required, is described below.  If $S$ is a
set of complex numbers, then $\real(S)$ and $\img(S)$ represent the
real and imaginary projections of $S$, respectively.  If $z$ is a
complex number, then $|z|$ denotes the absolute value of $z$.  On the
other hand, if $X$ is a complex matrix (or vector), then $\lt|X\rt|$
denotes the matrix (or vector) containing the absolute values of the
elements of $X$.  The diagonal square matrix containing the entries of
a complex vector $z$ along the diagonal is denoted by $\dg(z)$.  The
conjugate transpose of a matrix $V\in\mat{m}{n}{\complexset}$ is
denoted $\conjtranspose{V} = \lt(\real(V)-\iu\img(V)\rt)^T.$ If
$V\conjtranspose{V}$ is invertible, then
$\pinv{V}= \conjtranspose{V}\lt(V\conjtranspose{V}\rt)^{-1}$, which is
the pseudo-inverse of $V$.  Given two vectors $l,u\in\realset^k$, the
meet of the two vectors is denoted $l\bigwedge u$, defined as
$\lt(l\bigwedge u\rt)_i=\min\lt(l_i,u_i\rt)~\forall i\in\tup{k}$.  The
join is denoted $l\bigvee u$, defined as $\lt(l\bigvee
u\rt)_i=\max\lt(l_i,u_i\rt)~\forall i\in\tup{k}$.
