\vspace{0em}
\section{Conclusion}
We extended complex zonotopes to template complex zonotopes in order
to improve the efficiency of the computation of contractive sets and
positive invariants.  Template complex zonotopes retain a useful
feature of complex zonotopes, which is the scope to incorporate the
eigenvectors of linear dynamics among the generators because the
eigenstructure is related to existence of positive invariants.  In
addition, compared to complex zonotopes, the advantage template
complex zonotopes have is the ability to regulate the contribution of
each generator to the set by using the scaling factors.  Accordingly,
we proposed a systematic and more efficient procedure for verification
of stability of nearly periodic impulsive systems.  The advantage of
this new set representation is attested by the experimental results
that are better or competitive, compared to the state-of-the-art
methods and tools on benchmark examples. This work also contributes a
method for exploiting the eigenstructure of linear dynamics to
algorithmically determine template directions, required by most
verification approaches using template based set representations.  A
number of directions for future research can be identified. First, we
intend to extend these techniques to analysis to switched systems
under constrained switching laws. Also computationally speaking, our
approach is close in spirit to abstract interpretation. Indeed the
operations used to find contractive sets can be extended to invariant
computation for general hybrid systems with state-dependent discrete
transitions.

