
\input{packages}
\input{settings}
\input{macros}

\title{Template complex zonotopes for stability and invariant
  verification} 
\author{Arvind\ Adimoolam and Thao\ Dang
} 
\institute{\ Verimag,~Grenoble, France\\ \url{{santosh.adimoolam,thao.dang}@univ-grenoble-alpes.fr}.
}


\begin{document}
\maketitle


\begin{abstract}
Recently complex zonotopes were introduced as an extension of real
zonotopes to the complex domain, which could capture the eigenstructure
nearly periodic linear impulsive systems for stability
verification. %% They are used for stability verification of nearly
%% periodic linear impulsive systems by capturing the eigenstructure of
%% linear dynamics.
However, adding more generators to complex zonotopes distorts positive
invariance and consequently refining complex zonotopes in a verification
procedure is not easy. Therefore, in this paper we introduce a more
general set representation, called template complex zonotopes, where
the generators are fixed a-priori by a template, but the bounds on the
absolute values of their combining coefficients, called scaling
factors, are treated as variables and can be algorithmically
synthesized. %% Thus, complex zonotopes are a particular class of
%% template complex zonotopes with (fixed) unit scaling factors.
This flexibility in scaling factors leads to a more systematic and
significantly more efficient stability verification procedures in case
of template complex zonotope. Furthermore, the second contribution of
this paper is an application of template complex zonotopes to
verification of linear invariance properties of another class of
hybrid systems, namely linear switched systems with additive
disturbance. Experiments on a number of benchmark examples demonstrate
that our approach gives better or competitive results, compared to the
state-of-the-art methods and tools for these problems.
\end{abstract}

\section{Introduction}
\input{intro}
\input{litr}
\input{temp-comp-zon} 
\input{lis}
\input{system}  
\input{sw-exp}
\input{conclusion}

%\bibliographystyle{plain}
%\bibliography{ref,domain,mprt}



\begin{thebibliography}{10}

\bibitem{arvind2016lis}
A. Adimoolam and T. Dang.
\newblock Using complex zonotopes for stability verification.
\newblock In {\em American Control Conference}.
  sites.google.com/site/cztopepubs/, 2016.

\bibitem{AdjeGaubertGoubaultESOP2010}
A.~Adje, S.~Gaubert, and E.~Goubault.
\newblock Coupling policy iteration with semi-definite relaxation to compute
  accurate numerical invariants in static analysis.
\newblock In {\em ESOP}, volume 6012, pp 23--42, 2010.

\bibitem{DBLP:conf/aplas/AdjeGW15}
A. Adj{\'{e}}, P.{-}L .Garoche, and A. Werey.
\newblock Quadratic zonotopes - an extension of zonotopes to quadratic
  arithmetics.
\newblock In {\em APLAS 2015}, pp 127--145, 2015.

\bibitem{DBLP:conf/sas/AllamigeonGG08}
X. Allamigeon, S. Gaubert, and E. Goubault.
\newblock Inferring min and max invariants using max-plus polyhedra.
\newblock In {\em SAS}, LNCS 5079, pp 189--204.
  {Springer}, 2008.

\bibitem{allamigeon2015scalable}
X. Allamigeon, S. Gaubert, E. Goubault, S. Putot, and
  N. Stott.
\newblock A scalable algebraic method to infer quadratic invariants of switched
  systems.
\newblock In {\em Embedded
  Software}, pp 75--84. IEEE Press, 2015.

\bibitem{althoff2013}
M. Althoff.
\newblock Reachability analysis of nonlinear systems using conservative
  polynomialization and non-convex sets.
\newblock In {\em HSCC 2013}, pp 173--182. ACM, 2013.

\bibitem{bagrodzafSAS05}
R.~Bagnara, E.~Rodr{\'\i}guez-Carbonell, and E.~Zaffanella.
\newblock Generation of basic semi-algebraic invariants using convex polyhedra.
\newblock In {\em SAS 2005},
LNCS 3672, pp 19--34, Springer-Verlag, 2005.

\bibitem{BauLoo_NECSYS12a}
N.W. Bauer, S.J.L.M. van Loon, M.C.F. Donkers, N~van~de Wouw, and W.P.M.H.
  Heemels.
\newblock Networked control systems toolbox: Robust stability analysis made
  easy.
\newblock In {\em IFAC Workshop on Distributed Estimation and Control in
  Networked Systems (NECSYS)}, pp 55--60, 2012.

\bibitem{blanchini2015switching}
F. Blanchini and S. Miani.
\newblock Switching and switched systems.
\newblock In {\em Set-Theoretic Methods in Control}, pp 405--466. Springer,
  2015.

\bibitem{2013-briat-convex}
C. Briat.
\newblock Convex conditions for robust stability analysis and stabilization of
  linear aperiodic impulsive and sampled-data systems under dwell-time
  constraints.
\newblock {\em Automatica}, 49(11):3449--3457, 2013.

\bibitem{Cai2008}
C. Cai, R.~Goebel, and A.R. Teel.
\newblock Smooth lyapunov functions for hybrid systems part ii:
  (pre)asymptotically stable compact sets.
\newblock {\em IEEE Trans. on Automatic Control}, 53(3):734--748, 2008.

\bibitem{CousotCousot76-1}
P. Cousot and R. Cousot.
\newblock Static determination of dynamic properties of programs.
\newblock In {\em 2nd Int. Symp. Prog.}, pp 106--130. Dunod, 1976.

\bibitem{DBLP:conf/popl/CousotH78}
P. Cousot and N. Halbwachs.
\newblock Automatic discovery of linear restraints among variables of a
  program.
\newblock In {\em POPL}, pp 84--96, 1978.

\bibitem{DBLP:conf/aplas/DangG11}
T. Dang and T.M. Gawlitza.
\newblock Template-based unbounded time verification of affine hybrid automata.
\newblock In {\em APLAS 2011}, LNCS 7078, pp 34--49. Springer, 2011.

\bibitem{Feron2010}
E.~Feron.
\newblock From control systems to control software: Integrating
  lyapunov-theoretic proofs within code.
\newblock {\em IEEE Control Systems Magazine}, (1):50--71, December 2010.

\bibitem{2014-fiacchini-set}
M. Fiacchini and I.-C. Morarescu.
\newblock Set theory conditions for stability of linear impulsive systems.
\newblock In {\em CDC 2014}, IEEE, 2014.

\bibitem{2010-fridman-refined}
E. Fridman.
\newblock A refined input delay approach to sampled-data control.
\newblock {\em Automatica}, 46(2):421--427, 2010.

\bibitem{Fujioka2009}
H. Fujioka.
\newblock A discrete-time approach to stability analysis of systems with
  aperiodic sample-and-hold devices.
\newblock {\em IEEE Trans. on Aut. Control}, 54(10):2440--2445,
  2009.

\bibitem{HSCC05}
A. Girard.
\newblock Reachability of uncertain linear systems using zonotopes.
\newblock In {\em HSCC}, pp 291--305, 2005.

\bibitem{Goebel2009}
R.~Goebel, R.G. Sanfelice, and A.~Teel.
\newblock Hybrid dynamical systems.
\newblock {\em Control Systems, IEEE}, 29(2):28--93, 2009.

\bibitem{HetelDaafouz2006}
L.~Hetel, J.~Daafouz, and C.~Iung.
\newblock Stabilization of arbitrary switched linear systems with unknown
  time-varying delays.
\newblock {\em IEEE Trans. on Automatic Control}, 51(10):1668--1674,
  2006.

\bibitem{2013hetel}
L. Hetel, J. Daafouz, S. Tarbouriech, and C. Prieur.
\newblock Stabilization of linear impulsive systems through a nearly-periodic
  reset.
\newblock {\em Nonlinear Analysis: Hybrid Systems}, 7(1):4--15, 2013.

\bibitem{Hu2003}
L.~Hu, J.~Lam, Y.~Cao, and H.~Shao.
\newblock A  {LMI} approach to robust h2 sampled- data control for linear
  uncertain systems.
\newblock {\em IEEE Trans. Syst. Man Cybern.}, 33(1):149--155, 2003.

\bibitem{DBLP:conf/amcc/KaoW14}
C.{-}Y. Kao and D.{-}R. Wu.
\newblock On robust stability of aperiodic sampled-data systems - an integral
  quadratic constraint approach.
\newblock In {\em ACC 2014}, pp 4871--4876, 2014.

\bibitem{AlKhatib2015}
M. Al Khatib, A. Girard, and T. Dang.
\newblock Stability verification of nearly periodic impulsive linear systems
  using reachability analysis.
\newblock In {\em ADHS 2015}. ACM, 2015.

\bibitem{kouramas2005minimal}
K.I. Kouramas, S.V. Rakovi{\'c}, E.C. Kerrigan, J.C. Allwright, and D.Q. Mayne.
\newblock On the minimal robust positively invariant set for linear difference
  inclusions.
\newblock In {\em CDC-ECC'05}, pp 2296--2301. IEEE,
  2005.

\bibitem{KurzhanskiVaraiya00}
A.~Kurzhanski and P.~Varaiya.
\newblock Ellipsoidal techniques for reachability analysis.
\newblock In {\em HSCC}, volume 1790 of {\em {LNCS}}, pp 202--214.
  {Springer}, 2000.

\bibitem{DBLP:conf/pado/Mine01}
A. Min{\'e}.
\newblock A new numerical abstract domain based on difference-bound matrices.
\newblock In {\em PADO}, pp 155--172, 2001.

\bibitem{DBLP:journals/lisp/Mine06}
A. Min{\'e}.
\newblock The octagon abstract domain.
\newblock {\em Higher-Order and Symbolic Computation}, 19(1):31--100, 2006.

\bibitem{naghshtabrizi2007delay}
P.~Naghshtabrizi.
\newblock {\em Delay Impulsive Systems: A Framework for Modeling Networked
  Control Systems}.
\newblock University of California, Santa Barbara, 2007.

\bibitem{2008-naghshtabrizi-exponential}
P. Naghshtabrizi, J.P. Hespanha, and A.R. Teel.
\newblock Exponential stability of impulsive systems with application to
  uncertain sampled-data systems.
\newblock {\em Systems \& Control Letters}, 57(5):378--385, 2008.

\bibitem{nevsic2004framework}
D.~Ne{\v{s}}i{\'c} and A.R. Teel.
\newblock A framework for stabilization of nonlinear sampled-data systems based
  on their approximate discrete-time models.
\newblock {\em IEEE Transactions on Automatic Control}, 49(7):1103--1122, 2004.

%\bibitem{Omran2013}
%H.~Omran, L.~Hetel, J.-P. Richard, and F.~Lamnabhi-Lagarrigue.
%\newblock On the stability of input-affine nonlinear systems with sampled-data
%  control.
%\newblock In {\em ECC 2013}, pp 2585--2590,
%  2013.

\bibitem{polyak2006rejection}
B.T. Polyak, A.V. Nazin, M.V. Topunov, S. Nazin.
\newblock Rejection of bounded disturbances via invariant ellipsoids technique.
\newblock {\em CDC 2006}, pp 1429--1434. IEEE, 2006.

\bibitem{Rodriguez-Carbonell:2007}
E. Rodr\'{\i}guez-Carbonell and D. Kapur.
\newblock Automatic generation of polynomial invariants of bounded degree using
  abstract interpretation.
\newblock {\em Sci. Comput. Program.}, 64(1):54--75, January 2007.

\bibitem{VMCAI05}
S. Sankaranarayanan, H.B. Sipma, and Z. Manna.
\newblock Scalable analysis of linear systems using mathematical programming.
\newblock In {\em VMCAI}, pp 25--41, 2005.

\bibitem{2012-seuret-novel}
A. Seuret.
\newblock A novel stability analysis of linear systems under asynchronous
  samplings.
\newblock {\em Automatica}, 48(1):177--182, 2012.

\bibitem{Teel1998}
A.~Teel, D.~Nesic, and P.V. Kokotovic.
\newblock A note on input-to-state stability of sampled-data nonlinear systems.
\newblock In {\em CDC 1998}, pp 2473--2478, IEEE, 1998.

\bibitem{wittenmark2002computer}
B. Wittenmark, K.~J. Astrom, and K.-E. Arzen.
\newblock Computer control: An overview.
\newblock {\em IFAC Professional Brief}, 1 2002.

\bibitem{Mikheev1988}
Y.V. Mikheev, V.A. Sobolev, and E.M. Fridman.
\newblock Asymptotic analysis of digital control systems.
\newblock {\em Automation and Remote Control}, 49(9):1175--1180, 1988.

\bibitem{grant2008cvx}
Grant, Michael and Boyd, Stephen and Ye, Yinyu.
  \newblock {CVX: Matlab software for disciplined convex programming, 2008.}
  

\end{thebibliography}





\end{document}
























