We shall now describe some general properties of support functions of
convex sets and also some specific properties related to interval
zonotopes and sub-parallelotopes.  These properties shall be used
later to derive an over-approximation of the intersection of Minkowski
sum of a convex set and interval zonotope with a sub-parallelotope.
We use the following notation for the rest of
this chapter, unless otherwise specified.
%
\begin{align*}
& \lb,\ub\in\reals^k:
  k\leq n,~~~\plb\in\lt(\reals\bigcup\set{-\infty}\rt)^k,~~~\pub\in\lt(\reals\bigcup\set{\infty}\rt)^k\\
& ~~~\qtemp\in\mat{k}{n}{\reals}:~\lt(\qtemp\qtemp^T\rt)~\text{is
non-singular}
\end{align*}
%
The following properties are some properties of the support function
of a convex set.
%
\begin{lemma}~\label{lem:gen-supp}
All of the following statements are true about any two convex subsets
$\Psi_1,\Psi_2$ of $\reals^n$ and any $v\in\reals^n$.
%
\begin{enumerate}
\item $\supp{v}{\Psi_1\oplus\Psi_2}=\supp{v}{\Psi_1}+\supp{v}{\Psi_2}$.
\item If $\Psi_1\bigcap\Psi_2\neq\emptyset$, then $\supp{v}{\Psi_1\bigcap\Psi_2}\leq\inf\set{\supp{v}{\Psi_1},\supp{v}{\Psi_2}}$.
\end{enumerate}
%
\end{lemma}
%
\begin{proof}
We derive the following to prove the first statement.
%
\begin{align*}
& \supp{v}{\Psi_1\oplus\Psi_2} =
  \sup_{x\in\Psi_1,~y\in\Psi_2}v^T(x+y)\\
& = \sup_{x\in\Psi_1}v^Tx+\sup{x\in\Psi_2}v^Ty=\supp{v}{\Psi_1}+\supp{v}{\Psi_2}. 
\end{align*}
%
To prove the second statement, we derive the following.
%
\begin{align*}
& \supp{v}{\Psi_1\bigcap\Psi_2}=\sup_{x\in\Psi_1\bigcap\Psi_2}v^Tx\\
& \leq
  \inf\set{\sup{x\in\Psi_1}v^Tx,\sup{x\in\Psi_2}v^Tx}\\
& = \inf\set{\supp{v}{\Psi_1},\supp{v}{\Psi_2}}.~\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
When the support function of a sub-parallelotope is finite, then we
get the following result.
%
\begin{lemma}~\label{lem:exist-point}
Let $v\in\reals^n$ be such that
$\supp{v}{\ptope{\qtemp}{\plb}{\pub}}<\infty$.  Then there exists
$p\in\iztope{\pinv{\qtemp}}{\maxapprox{\lb}{\plb}}{\minapprox{\lb}{\plb}}$
  such that $\supp{v}{\ptope{\qtemp}{\plb}{\pub}}=v^Tp$.
\end{lemma}
%
\begin{proof}
According to Lemma~\ref{lem:ptope-iz-conversion}, we get
%
\[
\ptope{\qtemp}{\plb}{\pub}=\set{\pinv{\qtemp}\zeta:~\zeta\in\reals^k,~\plb\leq\zeta\leq\pub}\oplus\nullspace{\qtemp}.
\]
%
Therefore,
we derive the following using Lemma~\ref{lem:gen-supp} for computing
the Minkowski sum of two sets
%
\begin{align*}
&
  \supp{v}{\ptope{\qtemp}{\plb}{\pub}}=\sup\set{v^T\pinv{\qtemp}\zeta:~\zeta\in\reals^k,~\plb\leq\zeta\leq\pub}+\supp{v}{\nullspace{\qtemp}}\\
& =  \sum_{i=1}^k\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih+\supp{v}{\nullspace{\qtemp}}.
\end{align*}
%
As $\nullspace{\qtemp}$ is a vector space, so
$\supp{v}{\nullspace{\qtemp}}$ can either be zero or infinity.
However, we are given that
$\supp{v}{\ptope{\qtemp}{\plb}{\pub}}<\infty$.  So,
$\supp{v}{\nullspace{\qtemp}}=0$.  Then we get,
%
\begin{align*}
&
  \supp{v}{\ptope{\qtemp}{\plb}{\pub}}=\sum_{i=1}^k\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih.~\numberthis\label{eqn:proof-suppint2}
\end{align*}
%
Let us define
$\zeta\in\reals^k:~\maxapprox{\lb}{\plb}\leq\zeta\leq\minapprox{\ub}{\pub}$
as follows.  For any $i\in\set{1,\ldots,k}$,
%
\[
\zeta_i=\lt\{\begin{array}{l}
\lt(\maxapprox{\lb}{\plb}\rt)_i~\text{if}~\lt(v^T\qtemp\rt)_i\leq 0\\
\lt(\minapprox{\ub}{\pub}\rt)_i~\text{otherwise}.
\end{array}
\rt.
\]
%
Then we shall prove that for any $i\in\set{1,\ldots,k}$,
%
\begin{equation}~\label{eqn:proof-suppint1}
\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih = \lt(v^T\pinv{\qtemp}\rt)_i\zeta_i.
\end{equation}
%
We shall prove Equation~\ref{eqn:proof-suppint1} by considering the following three cases.

{\it Case 1  :}  Let us consider that $\lt(v^T\qtemp\rt)_i<0$.  Then
$\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih=\lt(v^T\pinv{\qtemp}\rt)_i\plb_i$.
However, $\lt(v^T\pinv{\qtemp}\rt)_i\plb_i<\infty$ because
$\supp{v}{\ptope{\qtemp}{\plb}{\pub}}$ is finite.  Therefore,
$\plb_i>-\infty$.  Then $\plb_i=\maxapprox{\lb}{\plb}=\zeta_i$.  

{\it Case 2:  } Let us consider that $\lt(v^T\qtemp\rt)_i>0$.  Then
$\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih=\lt(v^T\pinv{\qtemp}\rt)_i\pub_i$.
However, $\lt(v^T\qtemp\rt)_i\plb_i<\infty$ because
$\supp{v}{\ptope{\qtemp}{\plb}{\pub}}$ is finite.  Therefore,
$\plb_i<\infty$.  Then $\pub_i=\maxapprox{\lb}{\pub}=\zeta_i$.  

{\it Case 3:  }  Let us consider that $\lt(v^T\qtemp\rt)_i=0$.  Then
%
\[
\sup_{h\in[\plb_i,\pub_i]}\lt(v^T\pinv{\qtemp}\rt)_ih=\lt(v^T\pinv{\qtemp}\rt)_i\pub_i
= 0 = \lt(v^T\pinv{\qtemp}\rt)_i\zeta_i.
\]
%
Let us consider $p=\pinv{\qtemp}\zeta$.  Then we derive using
Equations~\ref{eqn:proof-suppint2} and~\ref{eqn:proof-suppint1}
%
\begin{align*}
\supp{v}{\ptope{\qtemp}{\plb}{\pub}} = \sum_{i=1}^k\lt(v^T\pinv{\qtemp}\rt)_i\zeta_i=\pinv{\qtemp}\zeta.~\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%

The following lemma describes a condition when finite values of the
support function of a sub-parallelotope is less than that of an
interval zonotope.
%
\begin{lemma}~\label{lem:min-support}
Let $v\in\reals^n$ be such that
$\supp{v}{\ptope{\qtemp}{\plb}{\pub}}<\infty$.  Then,
%
\[
\supp{v}{\ptope{\qtemp}{\plb}{\pub}}\leq\supp{v}{\iztope{\pinv{\qtemp}}{\maxapprox{\lb}{\plb}}{\minapprox{\ub}{\pub}}}.
\]
%
\end{lemma}
%
\begin{proof}
The above lemma follows from the fact that by
Lemma~\ref{lem:exist-point}, there exists
$p\in\iztope{\pinv{\qtemp}}{\maxapprox{\lb}{\plb}}{\minapprox{\lb}{\plb}}$
such that $\supp{v}{\ptope{\qtemp}{\plb}{\pub}}=v^Tp$.  
\end{proof}
%
Now we shall derive an over-approximation for the intersection of the
Minkowski sum of a convex set and an interval zonotope with a
sub-parallelotope.
%
\begin{lemma}
Let $S$ be a convex set such that $0\in S$.  Let us consider that
${\lb\leq\maxapprox{\lb}{\plb}\leq\minapprox{\ub}{\pub}\leq\ub}$.  Then the following is
true.
%
\[
\lt(S\oplus\iztope{\pinv{\qtemp}}{\lb}{\ub}\rt)\bigcap\ptope{\qtemp}{\plb}{\pub}\subseteq
S\oplus\iztope{\pinv{\qtemp}}{\maxapprox{\lb}{\plb}}{\minapprox{\ub}{\pub}}. 
\]
%
\end{lemma}
%
\begin{proof}
Let us denote $\Psi_1=\iztope{\pinv{\qtemp}}{\lb}{\ub}$,
$\Psi_2=\ptope{\qtemp}{\plb}{\pub}$, and 
$\Psi_3=\iztope{\pinv{\qtemp}}{\maxapprox{\lb}{\plb}}{\minapprox{\ub}{\pub}}.$
We shall first prove that for any $v\in\reals^n$,
%
\begin{equation}
\supp{v}{\lt(S\oplus\Psi_1\rt)\bigcap\Psi_2}\leq
\supp{v}{S\oplus\Psi_3}.
\end{equation}
%
Let us denote $\supp{v}{S}=a$, $\supp{v}{\Psi_1}=b$ and
$\supp{v}{\Psi_2}=c$ and $\supp{v}{\Psi_3}=d$.  Since $0\in S$, so
$a\geq 0$.  Then we derive the following using
Lemma~\ref{lem:gen-supp}
%
\begin{align*}
& \supp{v}{\lt(S\oplus \Psi_1\rt)\bigcap\Psi_2}\leq \inf\set{a+b,c}\\
  & \%\%~~\text{As}~a\geq 0\\
& \leq\inf\set{a+b,a+c}=a+c.
\end{align*}
%
As an interval zonotope is a bounded set, $b<\infty$.  By
Lemma~\ref{lem:min-support}, if $c<\infty$, then $c<b$.  Therefore, we
get
%
\begin{align*}
& \supp{v}{\lt(S\oplus \Psi_1\rt)\bigcap\Psi_2}\leq
  \inf\set{a+b,c}\leq a+c.
\end{align*}
%
Next, we derive the following.
%
\begin{align*}
\supp{v}{S\oplus\lt(\Psi_1\bigcap\Psi_2\rt)}
\end{align*}
%
\end{proof}
%
