
Simple zonotopes are linear
projections of higher dimensional unit hypercubes onto lower
dimensional spaces, therefore a sub-class of polytopes.  A simple
zonotope is represented is a linear combination of real valued vectors
plus a center, such that the real valued combining co-efficients are
contained in a unit hypercube.  Geometrically speaking, a simple
zonotope is a Minkowski sum of line segments.
%
\begin{definition}[Simple zonotope]
Let us consider $\ptemp\in\reals^m$, whose column vectors are called
\emph{generators}, and $\cen\in\reals^n$ called the \emph{center}.  The following is the
representation of a real zonotope.
%
\begin{align*}
\rztope{\ptemp}{\cen}:=\set{\cen+\ptemp\zeta:~\zeta\in[0,1]^m}.
\end{align*}
%
\end{definition}
%
For the rest of this chapter, we
use the notation $\ptemp\in\reals^m$ and $\cen\in\reals^n$, unless
otherwise sepcified.

A main advantage of the zonotope set representation is that besides
being closed under linear transformation and Minkowski sum, these
operations can be computed efficiently.  The computation of linear
transformation of a zontope is given below.
%
\begin{lemma}[Linear transformation]
Let $A\in\mat{n}{n}{\reals}$.  Then
%
\begin{align*}
A\rztope{\ptemp}{\cen}=\rztope{A\ptemp}{A\cen}.
\end{align*}
%
\end{lemma} 
%
\begin{proof}
We derive the following.
%
\begin{align*}
&
  A\rztope{\ptemp}{\cen}=A\set{\cen+\ptemp\zeta:~\zeta\in[0,1]^m}\\
& = \set{A\cen+A\ptemp\zeta:~\zeta\in[0,1]^m}=\rztope{A\ptemp}{A\cen}.\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
The Minkowski sum of two zonotopes can be computed as follows.
%
\begin{lemma}[Minkowski sum]
Let us consider two matrices $\ptemp\in\mat{n}{m}{\reals}$ and
$\ptemp^\pr\in\mat{n}{r}{\reals}$.  Then the following is true.
%
\begin{align*}
& \rztope{\ptemp}{\cen}\oplus\rztope{\ptemp^\pr}{\cen^\pr}
= \rztope{\mymatrix{\ptemp & \ptemp^\pr}}{\cen+\cen^\pr}.  
\end{align*}
%
\end{lemma}
%
\begin{proof}
We derive the following.
%
\begin{align*}
& \rztope{\ptemp}{\cen}\oplus\rztope{\ptemp^\pr}{\cen^\pr}\\
& = \set{\cen+\ptemp\zeta:~\zeta\in[0,1]^m}\oplus\set{\cen^\pr+\ptemp^\pr\zeta^\pr:~\zeta^\pr\in[0,1]^r}\\
& =
  \set{\lt(\cen+\cen^\pr\rt)+\ptemp\zeta+\ptemp\zeta^\pr:~\zeta\in[0,1]^m,~\zeta^\pr\in[0,1]^r}\\
& = \set{\lt(\cen+\cen^\pr\rt)+\mymatrix{\ptemp
      &\ptemp^\pr}\mymatrix{\zeta\\\zeta^\pr}:~{\mymatrix{\zeta\\\zeta^\pr}}\in[0,1]^{m+r}}\\
& =  \rztope{\mymatrix{\ptemp & \ptemp^\pr}}{\cen+\cen^\pr}.\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
We have earlier discussed that
for a $V$-representation of a polytope, the complexity of Minkowski
sum operation is quadratic, while for a $H$-representation, the
complexity of Minkowski sum can be exponential.  On the other hand,
the complexity of both Minkowski sum and linear transformation
operations for a zonotope is only linear.  This is an advantage of the
zonotope representation compared to a general convex polytope
representation.  Therefore, simple zonotopes have been sucessfully
applied for bounded time computation of uncertain linear systems and
some affine hybrid systems with simple switching
conditions~\cite{makhlouf2014networked,Girard05reachabilityof,girard2008zonotope}.
However, for unbounded time computation of reachable sets, which
generally requires computing positive invariants, zonotopes have the
following drawback.  For the simple case of a stable linear system, we
do not know if a positively invariant non-zero zonotope exists.  Even
if such a positively invariant zonotope exists, similar to polytopes,
the complexity of computation can be arbitrarily high in any dimension
because they are geometrically a sub-class of polytopes.  But for a
particular case when a stable linear system (say discrete time) has
real eigenvalues, we can easily find a positively invariant zonotope
zonotope based on the following proposition.
%
\begin{proposition}
Let us consider $\ptemp\in\mat{n}{n}{\reals}$ consists
of the real eigenvectors of a matrix $A\in\mat{n}{n}{\reals}$ as
its column vectors, where $\mu\in[0,1]^n$ is the vector of real
eigenvalues, i.e., $A\ptemp
= \ptemp\diagonal{\mu}$.  Then,
$A\lt(\rztope{\ptemp}{0}\rt)\subseteq \rztope{\ptemp}{0}$.
\end{proposition}
% 
\begin{proof}
We derive
  %
\begin{align*}
& A\lt(\rztope{\ptemp}{0}\rt) = A\set{\ptemp\zeta:~\zeta\in[0, 1]^n}\\
&
=\set{A\ptemp\zeta:~\zeta\in[0,1]^n}=\set{V\diagonal{\mu}\zeta:~\zeta\in[0,1]^n}.~\numberthis\label{proof-eigzonotope}
\end{align*}
%
Let $y$ be a point
in $\rztope{\ptemp}{0}$.  By Equation~\ref{proof-eigzonotope}, we get
%
\begin{align*}
  &\exists\delta\in[0,1]^n:~y = \ptemp\diagonal{\mu}\delta.
\end{align*}
%
Let $\zeta = \diagonal{\mu}\delta$. Since $\mu\in[0,1]^n$ and
$\delta\in[0,1]^n$, we get $\zeta=\diagonal{\mu}\delta\in[0,1]^n$.  So,
%
\begin{align*}
  & y=\ptemp\zeta~~\text{ where }~
  \zeta\in[0,1]^n\\
  &\therefore~y\in\rztope{\ptemp}{0}.
\end{align*}
%
As the above is true for any $y\in
A\rztope{\ptemp}{0}$, we get
$A\lt(\rztope{\ptemp}{0}\rt)\subseteq
\rztope{\ptemp}{0}$ when $\infnorm{\mu}\leq 1$.
\end{proof}
%
However, the eigenvalues of a linear matrix can have non-zero
imaginary part, in addition to the real part.  Whereas, simple
zonotopes are defined on real numbers.  So, when the eigenvalues are
complex valued, we can not rely on the above proposition to find a
positive invariant.  Therefore, in the next chapter we introduce
complex zonotopes that can capture contraction along complex vectors.

Another drawback of simple zonotopes is that they not closed under
mutual intersection and intersection with half-spaces.  The
computation of intersection with half-spaces and hyperplanes is
required in reachability analysis of hybrid systems having linear
guards (pre-conditions) for switching.  To compute the intersection,
we can try to convert a zonotope to a polytope, compute the
intersection with the polytope and over-approximate the intersection
by another zonotope.  However, a zonotope with $m$ generators in an
$n$ dimensional space can have as many as
$2\lt(\begin{matrix}m\\n-1\end{matrix}\rt)$
faces~\cite{zaslavsky1975facing}, which is exponential in $n$.
Therefore, the conversion of a zonotope to a polytope can be
intractable in higher dimensions.  To address this problem, an
algorithm for the tight over-approximation of the intersection between
a zonotope and a hyperplane is proposed in~\cite{girard2008zonotope},
that is based on the projection of the zonotope onto 2-dimensional
hyperplanes.  Aleternatively, to extend the zonotope to a more general
set representation in which the intersection with a half-space is a
closed operation and can be computed efficiently.  Contrained
zonotopes~\cite{scott2016constrained}, constrained affine sets~\cite{Ghorbal2010} and
zonotopic bundles~\cite{althoff2011zonotope} are examples of such extensions.

In a constrained zonotope, there are linear equality constraints in
addition to the unit interval bounds on the combining coefficients.
Therefore, the intersection of a hyperplane and a constrained zonotope
can be represented by another constrained zonotope.  Moreover, they
retain the closure property under linear transformation and Minkowski
sum, which can also be computed efficiently.
%
\begin{definition}[Constrained zonotope]~\cite{scott2016constrained}
A constrained zonotope is represented by a tuple
$\lt(\ptemp,\cen,A,b\rt)$, where $\ptemp\in\mat{n}{m}{\reals}$,
$A\in\mat{k}{m}{\reals}$, $\cen\in\reals^n$ and $b\in\reals^m$, and
the tuple is assigned to the set
%
\[\set{\cen+\ptemp\zeta:\zeta\in[0,1]^m,A\zeta=b}.\]
%
\end{definition}
%
An even more general representation is a constrained affine
set~\cite{Ghorbal2010}, where the combining coefficients can range in some
abstract domain.  To represent the intersection of a contrained affine
set with half-spaces, the abstract domain constraining the combining
coefficients can be chosen such that it has linear relations.  Another
generalization is a zonotopic bundle set representation~\cite{althoff2011zonotopex},
which is closed under mutual intersection.

To approximate non-linear transformations of zonotopes, they have been
extended to quadratic zonotopes~\cite{DBLP:conf/aplas/AdjeGW15}, and more generally, polynomial
zonotopes~\cite{DBLP:conf/hybrid/Althoff13}. 
%
\begin{definition}~\cite{DBLP:conf/hybrid/Althoff13}
Let $f\in\polyring{x_1,\ldots,x_n}{\reals}$.  The following is a
polynomial zonotope.
%
\[\set{f(x):~x\in[-1,1]^n}.\]
%
\end{definition}
%
Although a polynomial zonotope and the complex zonotope that we
introduce in the next chapter are both non-polytopic sets, however,
both representations are geometrically different.  While a polynomial
zonotope is a polynomial function of real valued intervals, we shall
describe  a complex zonotope as a complex valued linear function
of circles in the complex plane.
