I have learned a lot through discussions with my adviser Dr. Thao
Dang.  She has inspired me by explaining many interesting research
problems.  I had the flexibility to work on any topic, which provided
me a wide exposure.  Her constant enthusiasm for research has been a
motivating factor.  She has also been a very friendly and
light-hearted person.  I remain grateful to her for providing me the
opportunity to work under her supervision and thank her for the
valuable time she has invested in guiding me.

I had the valuable opportunity to exchange ideas with the members of
MALTHY project.  Especially, I would like to thank Dr. Tristan Le Gall
for inviting me to CEA Saclay at the beginning of my research.
Some of the essential ideas in my research have been developed during
the visit.  I also thank him for showing me around Paris and making
the time enjoyable.

My interaction with the research team at Toyota in North America has
given me very valuable exposure to the problems relevant to industry.
I am thankful to Jim Kapinski, Xiaoqing Jin and Jyotirmoy Deshmukh for
inviting to visit Toyota and collaborating with me in research.  I
would like to thank Alexandre Donz\'e for the ideas that we have
discussed, his research collaboration and help with the Breach
toolbox.

I would like to thank Prof. Sylvie Putot and Prof. Mahesh Viswanathan
for agreeing to review my dissertation.

My interaction with the researchers and colleagues at VERIMAG has been
very fruitful.  I wish to thank Marcelo Forets for giving time to
together ponder over research problems and his keen interest in my
ideas.  I want to thank Dr. Oded Maler for organizing the group
meetings through which I could get to know about new research
directions.  I would like to thank my friends Dogan, Alexandre,
Nikolaos, Irini and Alexey, the researchers, colleagues and staff at
VERIMAG for creating a lively work atmosphere.  I thank my friend
Deepankar for the fun times and his support.


I am thankful to my parents for their love and always encouraging me.
