

    Since computers work with digital signals and the physical system
    they control operates in the analog world, sampling is required.
    Various parameters related to sampling of the system can be
    subject to uncertainty like the sampling period, delay, digital
    output of the controller, output feedback from the system, etc.
    These uncertainties can lead to instability of the system.
    Henceforth, we are faced with the challenge of verifying system
    stability in the presence of these uncertainties.  We address this
    issue by considering the problem of verifying stability of
    nearly-periodic impulsive systems, which can be used to model
    sampled-data systems \cite{naghshtabrizi2007delay} and networked
    control systems \cite{2008-naghshtabrizi-exponential}.  This
    problem has been tackled using control approaches, which mainly
    involve deriving stability conditions in terms of Lyapunov
    functions and checking these conditions using optimization (Linear
    Matrix Inequalities (LMI) or Sum of Squares (SOS)). In this work,
    we use a stability condition based on set contractiveness proposed
    in
    \cite{athanasopoulos2014alternative,2014-fiacchini-set,AlKhatib2015}
    and propose a new method for checking it using computational
    techniques, inspired by hybrid systems verification
    techniques. Globally exponential stability (GES) of
    nearly-periodic linear impulsive systems can be proved by showing
    the contractiveness of a compact and convex set containing the
    origin in its interior, also called as a $C$-set
    \cite{Lazar2013,athanasopoulos2014alternative,2014-fiacchini-set,AlKhatib2015}.
    The uncertainty in impulse times for which stability can be proved
    depends on the choice of the contractive $C$-set.  A
    nearly-periodic linear impulsive system is stable only if all of
    its reachability operators, which compute the state reached after
    an impulse, are stable.  This motivates us to use complex
    zonotopes since we can find good candidate complex zonotope for
    contractive sets using the eigenvectors of the reachability
    operators.  For proving stability condition, we consider complex
    zonotopes whose generator sets are chosen among the eigenvectors
    of reachability operators of the nearly-periodic linear impulsive
    system.  We then derive a condition for the contractiveness of a
    complex zonotope that can be verified by convex optimization.
    Concerning experimental results, our approach is either
    competitive or better compared to the existing approaches, in
    terms of the largeness of uncertainty of sampling periods for
    which stability could be proved.

    The chapter is organized into five main sections.  We discuss the
    related work in Section~\ref{lis-rel}.  In
    Section~\ref{sec:dynamics}, we describe the dynamics of a
    nearly-periodic linear impulsive system.  In
    Section~\ref{sec:ges}, we explain global exponential stability,
    the verification problem and its relation to finding a contractive
    $C$-set of the system.  In Section~\ref{sec:alg}, we explain our
    algorithm for stability verification based on complex zonotopes.
    The experiments on two benchmark examples are discussed in Section~\ref{sec:experiments}



\section{Related work}~\label{lis-rel}
A major approach to stability analysis of aperiodic sampling control uses time-delay 
systems, and stability can be proved using Lyapunov Krakovskii functional 
\cite{Mikheev1988,Teel1998,2010-liu-stability,Mazenc2013}, 
or time-dependent Lyapunov functional \cite{2010-fridman-refined}. Using a continuous-time model,  
discrete-time Lyapunov functions is proposed for stability condition \cite{2012-seuret-novel}, 
which can be checked using Sum of Squares (SOS) \cite{2013-seuret-stability}. Robust stability with respect to 
time-varying input delay can also be handled by input/output approach 
\cite{Mirkin2007,DBLP:journals/automatica/Fujioka09,DBLP:conf/amcc/KaoW14,Omran2013,Omran2014}.
Another important approach is based on the hybrid systems modeling framework, in particular time-varying impulsive systems 
\cite{Hu2003,nevsic2004framework,Goebel2009,Cai2008,BauLoo_NECSYS12a} and employs Lyapunov-based 
methods in various forms including discontinuous time-independent \cite{2008-naghshtabrizi-exponential} 
or time-dependent Lyapunov functions \cite{2010-fridman-refined}. Another popular 
approach involves using convex embedding \cite{HetelDaafouz2006,Fujioka2009,HetelKruszewski2011,2013hetel,Omran2014}. 
In this approach, stability tests can be formulated as parametric Linear Matrix Inequalities (LMIs) \cite{HetelDaafouz2006}, 
or as set contractiveness (such as, polytopic set contractiveness is equivalent to polyhedral Lyapunov 
functions) \cite{2014-fiacchini-set,2013-briat-convex,Lazar2013,athanasopoulos2014alternative,AlKhatib2015}. 
In this work, we focus on exponential stability and are inspired by
set theory conditions
\cite{2014-fiacchini-set,athanasopoulos2014alternative,AlKhatib2015} to derive a stability condition which is more conservative 
but can be efficiently verified. The novelty of our work lies in the use of complex zonotopes to efficiently 
find contractive sets. Computationally speaking, our approach is close in spirit to abstract interpretation
and hybrid systems analysis. Indeed the way we find contractive sets using such zonotopes is similar 
to the way invariant sets are computed using some zonotope
\cite{Girard05reachabilityof,Althoff2011,DBLP:conf/sas/GoubaultPV12} and
template-polyhedral abstract domains \cite{Sriram2008,jeannet2009apron}.



\section{Dynamics}~\label{sec:dynamics}
\input{chapters/sections-ch-lis/system.tex}

\section{Globally exponential stability and set contraction}~\label{sec:ges}
\input{chapters/sections-ch-lis/stability.tex}

\section{Stability verification using complex zonotope}~\label{sec:alg}
\input{chapters/sections-ch-lis/verification.tex}

\section{Experiments}~\label{sec:experiments}
\input{chapters/sections-ch-lis/experiments.tex}
