In many verification problems, the safe set can be given linear
constraints.  In this case, to verify safety, we have to verify the
bounds on the reachable set of the system along the directions of the
normals to the bounding hyperplanes.  We shall call the boundedness of
the reachable set along a given set of directions as a {\it linear
invariance property}.  In other words, a linear invariance property is
a linear constraint that is true for all reachable states of the
system at all time instants.  We consider the problem of verifying a
linear invariance property of a discrete time affine hybrid system.
We show that a linear invariance property is equivalent to the
existence of a positive invariant containing the initial set and
satisfying the linear constraints of the invariance property. However,
the smallest positive invariant satisfying the property can be
computationally intractable to represent.  Alternatively, we can use a
set representation by which we can compute sufficiently accurate
positive invariants that verify the property.


We shall use augmented complex zonotopes to compute the positive
invariants.  As discussed earlier, complex zonotopes have the
advantage that they are closed under linear transformation and
Minkowski sum, and efficiently capture positive invariants for linear
systems using the complex eigenstructure.  Their representation is
generalized to augmented complex zonotopes to compute an
over-approximation of the intersection with linear guards such that
the support function can still be computed efficiently.  The efficient
computation of support function is crucial for verifying the
satisfaction of linear constraints given in a linear invariance
property.  We shall derive a convex program  for finding augmented
complex zonotope positive invariants to verify a linear invariance
property.  The derivation of the convex program uses the computations
on augmented complex zonotopes that we have developed earlier.

 This chapter is
organized into four main sections.  In
Section~\ref{sec:hybrid-system}, we describe a discrete time affine
hybrid system and positive invariants of the system.  In
Section~\ref{sec:linear-invariance}, we define a linear invariance
property and show its equivalence to the existence of a certain
positive invariant.  In Section~\ref{sec:verification-invariance}, we
derive a convex program for computing a positive invariant that
verifies a linear invariance property.  We also explain heuristics for
choosing the template of the augmented complex to leverage the
efficiency of the verification procedure.  In Section~\ref{sec:acz-exp},
we discuss experiments on three benchmark examples that demonstrate
the efficiency of our approach.

\section{Discrete time affine hybrid system}~\label{sec:hybrid-system}
\input{chapters/sections-ch-invariance/system.tex}

\section{Linear invariance property}~\label{sec:linear-invariance}
\input{chapters/sections-ch-invariance/property.tex}

\section{Verification using complex zonotope}~\label{sec:verification-invariance}
\input{chapters/sections-ch-invariance/verification.tex}

\section{Experiments}~\label{sec:acz-exp}
\input{chapters/sections-ch-invariance/experiments.tex}


