While computing positive invariants using a set representation,
ascertaining the positive invariance of a set requires deciding the
inclusion of the next reachable set inside the given set.  In the case
of complex zonotopes, we shall show that checking the exact inclusion
amounts to solving a is a non-convex optimization problem.  Therefore,
we later find a sufficient condition expressed by convex constraints
for checking the inclusion.  The convex constraints we derive later
are specifically second order conic constraints, which are described
below.
%
\begin{definition}[Second order conic constraint]
A second order conic constraint on a variable $x$ taking values in
$\reals^n$ is one of the following expressions.
\begin{enumerate}
\item $\sqnorm{Ax+b}\leq c^Tx+d$ where $A\in\mat{r}{n}{\reals}$,
  $b\in\reals^r$, $c\in\reals^n$ and $d\in\reals$.
\item $p^Tx=q$ where $p\in\reals^n$ and $q\in\reals$.
\end{enumerate}
\end{definition}
%
Given a set of second order conic constraints on a variable
$x\in\reals^n$, solving the constraints refers to finding a value
$x^*\in\reals^n$ that satisfies the constraints.  A value
$x^\pr\in\reals^n$ is called an approximate solution within a
precision $\epsilon\in\reals_{\geq 0}$ if there exists a solution
$x^*\in\reals^n$ such that $\sqnorm{x^\pr-x^*}\leq \epsilon$.  There
are numerical algorithms based on interior point methods~\cite{todo}
that can efficiently find approximate solutions with very high
precision to second order conic constraints (SOCC).

Checking inclusion of a single point inside a template complex
zonotope is equivalent to solving SOCC, as described below.
%
\begin{lemma}[Inclusion of a point]
Let us consider a point $x\in\compnums^n$.  Then
$x\in\tcztope{\ptemp}{\cen}{\sfact}\subset\compnums^n$ if and only if
all of the following is collectively true.
%
\begin{align}
& \exists\zeta\in\compnums^m:\nonumber\\
& \ptemp\zeta = x-c~\label{eqn:lem-point-inclusion-1}\\
& \absolute{\zeta}\leq \sfact.~\label{eqn:lem-point-inclusion-2}
\end{align}
%
\end{lemma}
%
\begin{proof}
The above result follows from the fact that any point 
$x\in\tcztope{\ptemp}{\cen}{\sfact}$ is of the form
$x=\cen+\ptemp\zeta$ for some $\zeta\in\compnums^m$ such that
$\absolute{\zeta}\leq \sfact$.
\end{proof}
%
Equation~\ref{eqn:lem-point-inclusion-1} is an equality constraint on
$\zeta$, which is therefore an SOCC.  We know that the absolute value
of a complex number is the square norm of a two dimensional vector.
So, Equation~\ref{eqn:lem-point-inclusion-2} is equivalent to a set of
square norm constraints on the real and imaginary components of
$\zeta$, which are therefore SOCC constraints.  Hence, the inclusion
of a point inside a template complex zonotope can be checked by
solving second order conic constraints.

Now we state the necessary and sufficient condition for checking
inclusion between two template complex zonotopes.
%
\begin{lemma}[Exact inclusion between template complex zonotopes]~\label{lem:exact-inclusion}
Let us consider $\ptemp\in\mat{n}{m}{\compnums}$ and
$\ptemp^\pr\in\mat{n}{r}{\compnums}$.  The inclusion
$\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$
holds if and only if
\begin{equation}\label{eqn:exact-inclusion}
\max_{\set{\zeta^\pr\in\compnums^{r}:\absolute{\zeta^\pr}\leq \sfact^\pr}}\min_{\set{\zeta\in\compnums^m:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}}\max_{i=1}^m\lt(\absolute{\zeta_i}-s_i\rt)\leq 0
\end{equation}
\end{lemma}
%
\begin{proof}
  We have
  %
  \begin{align*}
    &\tcztope{\ptemp}{\cen}{\sfact}=\set{\cen+\ptemp\zeta:~\zeta\in\compnums^m,~\absolute{\zeta}\leq\sfact},\\
    &\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}=\set{\cen^\pr+\ptemp^\pr\zeta^\pr:~\zeta^\pr\in\compnums^r,~\absolute{\zeta^\pr}\leq\sfact^\pr}.
  \end{align*}
  %
Therefore, we get
$\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$
if and only if
for every $\zeta^\pr\in\compnums^r:\absolute{\zeta^\pr}\leq \sfact^\pr$,
there exists
$\zeta\in\compnums^m:\ptemp\zeta+\cen=\ptemp^\pr\zeta^\pr+\cen^\pr~\wedge~\absolute{\zeta}\leq
\sfact$.  This is equivalently expressed as the constraint in Equation~\ref{eqn:exact-inclusion}.
\end{proof}
%
The reason solving Equation~\ref{eqn:exact-inclusion}
requires non-covex optimization is explained as follows.  Let us consider
that $\ptemp$ has a pseudo-inverse $\pinv{\ptemp}$.  Then by the
rank-nullity theorem
%
\[
\set{\zeta:~\ptemp\zeta=\ptemp\zeta^\pr+\cen^\pr-\cen}=\set{\pinv{\ptemp}\lt(\zeta^\pr-c\rt)+v:~v\in\nullspace{\ptemp}}
\]
%
So,
%
\begin{align*}
& \min_{\set{\zeta\in\compnums:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}}\max_{i=1}^m\lt(\absolute{\zeta_i}-s_i\rt)\\
&
=\min_{\set{v\in\nullspace{\ptemp}}}\max_{i=1}^m\lt(\absolute{\pinv{\ptemp}\lt(\zeta^\pr-c\rt)+v}-s_i\rt)
\end{align*}
%
The absolute value of a complex variable is a convex quadratic
function of the real and imaginary components of the variable.  So,
the above function is a point-wise minimum (for points $v$ in the null
space $\null{\ptemp}$) of a set of convex quadratic functions over
$\zeta^\pr$, which is therefore a non-concave function of $\zeta^\pr$.
So the maximization
%
\[
\max_{\set{\zeta^\pr\in\compnums^{r}:\absolute{\zeta^\pr}\leq \sfact^\pr}}\min_{\set{\zeta\in\compnums^m:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}}\max_{i=1}^m\lt(\absolute{\zeta_i}-s_i\rt)
\]
%
is equivalent to maximizing a non-concave function of $\zeta^\pr$.
Maximizing a non-concave function is a non-covex optimization problem.

We shall now derive a sufficient condition, equivalent to a set of
second order conic constraints, for checking inclusion between two
template complex zonotopes.  The following result is used to later derive
the sufficient condition.
%
\begin{lemma}~\label{lem:transfer-matrix}
  Let us consider ${\sfact\in\reals^m_{\geq 0}}$,
  ${\sfact^\pr\in\reals^r_{\geq 0}}$, ${\zeta^\pr\in\compnums^r}$,
  ${\cen,\cen^\pr\in\compnums^n}$,${\ptemp\in\mat{n}{m}{\compnums}}$, ${\ptemp^\pr\in\mat{n}{r}{\compnums}}$ 
  ${\absolute{\zeta^\pr}\leq\sfact^\pr}$,
  ${\tmat\in\mat{m}{r}{\compnums}}$  and ${y\in\compnums^m}$ such that
  %
  \begin{align*}
&
    \ptemp\tmat=\ptemp^\pr\diagonal{\sfact^\pr},\hspace{1em}\ptemp\tvect=\lt(c^\pr-c\rt).~\numberthis\label{eqn:inclusion1}
    \\
&\text{Then}\hspace{2em}\min_{\set{\zeta\in\compnums:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}}\max_{i=1}^m\lt(\absolute{\zeta_i}-\sfact_i\rt)\leq \max_{i=1}^m\lt(\absolute{\tvect_i}+\sum_{j=1}^r\absolute{\tmat_{ij}}-\sfact_i\rt).~\numberthis\label{eqn:transfer-matrix}
\end{align*}
%
\end{lemma}
%
\begin{proof}
  Let us consider $\epsilon\in\compnums^{r}$, xsuch that for any $i\in\set{1,...,r}$,
%
\[\left\{
\begin{array}{l}
\epsilon_i=\frac{\zeta^\pr}{s^\pr_i}~\text{if}~ s^\pr_i\neq 0\\
\epsilon_i=0~\text{otherwise}
\end{array}
\right..\]
%
From the above definition and the fact that $\absolute{\zeta^\pr}\leq
s^\pr$, we get $\zeta^\pr=\diagonal{s^\pr}\epsilon$ and
$\max_{j=1}^r\absolute{\epsilon_j}\leq 1$.  Then we derive
%
\begin{align*}
&\ptemp^\pr\zeta^\pr+c-c^\pr
=\ptemp^\pr\diagonal{\sfact^\pr}\epsilon+c-c^\pr
=\ptemp\tmat\epsilon+\ptemp\tvect
=\ptemp\lt(\tmat\epsilon+\tvect\rt)
\end{align*}
%
According the above equation,
%
\begin{align*}
& \tmat\epsilon+\tvect\in\set{\zeta\in\compnums:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}.\\
& \implies
  \min_{\set{\zeta\in\compnums:\ptemp\zeta=\ptemp^\pr\zeta^\pr+\cen^\pr-\cen}}\max_{i=1}^m\lt(\absolute{\zeta_i}-\sfact_i\rt)\leq
  \max_{i=1}^m\lt(\absolute{\lt(X\epsilon+y\rt)_i}-\sfact_i\rt)\\
&   ~~\%\%~\text{Using triangular inequality}\\
&\leq \max_{i=1}^m\lt(\absolute{\tvect_i}+\sum_{j=1}^r\absolute{\tmat_{ij}}\absolute{\epsilon_j}-\sfact_i\rt)\\
& ~~\%\%~\text{Since}~\max_{j=1}^r\absolute{\epsilon_j}\leq 1\\
& \leq  \max_{i=1}^m\lt(\absolute{\tvect_i}+\sum_{j=1}^r\absolute{\tmat_{ij}}-\sfact_i\rt).\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
We define the following relation between two template
complex zonotopes, which we shall prove is a sufficient condition for
the inclusion between them.
%
\begin{definition}[Relation for inclusion-checking]~\label{defn:inclusion-tcz}
Let us consider $\ptemp\in\mat{n}{m}{\compnums}$ and
$\ptemp^\pr\in\mat{n}{r}{\compnums}$.  We say
$\tcztope{\ptemp}{\cen}{\sfact}\order\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$
iff all of the following is collectively true.
%
\begin{align*}
& \exists \tmat\in\mat{m}{r}{\compnums},\tvect\in\compnums^m~~\text{such
that}\\
& \ptemp\tmat=\ptemp^\pr\diagonal{\sfact^\pr},~~\ptemp\tvect=\cen^\pr-\cen~\numberthis\label{eqn:inclusion-tcz1}\\
& \max_{i=1}^m\lt(\absolute{\tvect_i}+\sum_{j=1}^r\absolute{\tmat_{ij}}-\sfact_i\rt)\leq
0~\numberthis\label{eqn:inclusion-tcz2}.
\end{align*}
%
\end{definition}
%
\begin{theorem}[Sufficient condition for inclusion checking]~\label{thm:suff-inclusion}
  The following is true.
%
\begin{align*}
&  \tcztope{\ptemp}{\cen}{\sfact}\order\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\\
&\implies \tcztope{\ptemp}{\cen}{\sfact}\subseteq\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}.
\end{align*}
%
\end{theorem}
%
\begin{proof}
The theorem follows from Lemmas~\ref{lem:exact-inclusion}
and~\ref{lem:transfer-matrix}.  According to
Lemma~\ref{lem:exact-inclusion}, the inclusion
$\tcztope{\ptemp}{\cen}{\sfact}\subseteq\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$
holds iff the L.H.S of Equation~\ref{eqn:exact-inclusion} is bounded
above by zero.  According to Lemma~\ref{lem:transfer-matrix}, if there
exists a $\tmat$ and $\tvect$ satisfying
Equation~\ref{eqn:inclusion1}, then the R.H.S of
Equation~\ref{eqn:transfer-matrix} is an upper bound on the L.H.S of
Equation~\ref{eqn:exact-inclusion}.  So, if there exist $\tmat$ and
$\tvect$ satisfying Equation~\ref{eqn:inclusion1} such that the R.H.S
of Equation~\ref{eqn:transfer-matrix} is bounded above by zero, then
the inclusion holds.  The relation
$\tcztope{\ptemp}{\cen}{\sfact}\order\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$
implies that there exists $\tmat$ and $\tvect$ satisfying
Equations~\ref{eqn:inclusion1} such that the R.H.S of
Equation~\ref{eqn:transfer-matrix} is bounded above by zero.
\end{proof}
%
\begin{remark}
  We can write Equation~\ref{eqn:inclusion-tcz2} as
  %
  \[
\forall
i\in\set{1,...,m}~\absolute{\mymatrix{\real\lt(X^T_i\rt)\\\img\lt(X^T_i\rt)\\\real\lt(y_i\rt)\\\img\lt(y_i\rt)}}\leq\sfact_i,
  \]
%
  which is equal to $m$ second order conic constraints on a vector of
  size $mr+2m$, which comprises the scaling factors and the additional
  variables.  We see that Equation~\ref{eqn:inclusion-tcz2} is a set
  of $2n$ linear constraints on a vector of size $mr+2m+n$, which
  comprises the center, scaling factors and the additional variables.
  On the other hand, the representation size of both the template
  complex zonotopes together is $(m+r)n$.  Therefore, the size of the
  second order conic program for checking the inclusion between two
  template complex zonotopes can be at most of the order cubic in
  the size of the template complex zonotopes.
\end{remark}
%
%% Furthermore, the above relation is a partial order.
%
%% The relation ``$\order$'' is a partial order on the set of template
%% complex zonotopes, as stated in the following theorem.
%% %
%% \begin{theorem}[Partial ordering]
%% For any three template complex zonotopes\\
%% ${\tcz{\ptemp}{\cen}{\sfact},\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\text{
%%     and }\tcz{\ptemp^\dpr}{\cen^\dpr}{\sfact^\dpr}}$,
%% all of the following conditions are true.
%% %
%% \begin{enumerate}
%% \item Reflexivity:
%% $\tcz{\ptemp}{\cen}{\sfact}\order\tcz{\ptemp}{\cen}{\sfact}$.
%% \item Anti-symmetry: If~
%% $\tcz{\ptemp}{\cen}{\sfact}\order\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$
%% and
%% $\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\order\tcz{\ptemp}{\cen}{\sfact}$,
%% then
%% $\tcz{\ptemp}{\cen}{\sfact}=\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$.
%% \item Transitivity: If~
%% $\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\order\tcz{\ptemp}{\cen}{\sfact}$
%% and
%% $\tcz{\ptemp^\dpr}{\cen^\dpr}{\sfact^\dpr}\order\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}$,
%% then $\tcz{\ptemp^\dpr}{\cen^\dpr}{\sfact^\dpr}\order\tcz{\ptemp}{\cen}{\sfact}$.
%% \end{enumerate}
%% %
%% \end{theorem}

%% \begin{proof}
%% We prove reflexivity, antisymmetry and transitivity separately as follows.
%% \begin{enumerate}
%% \item {\it Reflexivity}:  Let us consider
%%   %
%%   \begin{align*}
%% &  \tmat=\diagonal{\sfact}\text{ and }
%%   \tvect=\repmat{m}{1}{0}.\\
%% &\text{Then we get }~\ptemp\tmat=\ptemp\diagonal{\sfact},~~
%% \ptemp\tvect=0=c-c\text{ and }\\
%% & \max_{i=1}^m\lt(\absolute{y_i}+\sum_{j=1}^m\absolute{X_{ij}}-\sfact_i\rt)
%% =\max_{i=1}^m\lt(0+\sfact_i-\sfact_i\rt)=0\\
%% & \text{So}, \tcz{\ptemp}{\cen}{\sfact}\order\tcz{\ptemp}{\cen}{\sfact}.
%% \end{align*}
%% %
%% \item {\it Anti-symmetry}: Let us consider that
%% %
%% \begin{align*}
%% &
%% \tcz{\ptemp}{\cen}{\sfact}\order\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}
%% \text{ and }
%% \tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\order\tcz{\ptemp}{\cen}{\sfact}.\\
%% & \text{Then by Theorem~\ref{thm:suff-inclusion}, we get}\\ 
%% & \tcz{\ptemp}{\cen}{\sfact}\subseteq\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}
%% \text{ and }
%% \tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\subseteq\tcz{\ptemp}{\cen}{\sfact}\\
%% &\implies
%% \tcz{\ptemp}{\cen}{\sfact}=\tcz{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}.
%% \end{align*}
%% %
%% \item {\it Transitivity:}  
%% \end{enumerate}
%% \end{proof}


When the template of the complex zonotope inside which containment is
checked is invertible, and the centers of the template complex
zonotope are same, then the above sufficient condition for inclusion
checking is also a necessary condition.  This is described in the
following theorem.
%
\begin{theorem}
Let us consider
$\ptemp\in\mat{n}{n}{\compnums}$ and
$\ptemp^\pr\in\mat{n}{m}{\compnums}$ such that $\ptemp$ is a non-singular matrix.
Then
$\tcztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$
if and only if
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\order\tcztope{\ptemp}{\cen}{\sfact}$.
\end{theorem}
%
\begin{proof}
By Theorem~\ref{thm:suff-inclusion}, we know that if
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\order\tcztope{\ptemp}{\cen}{\sfact}$
is true,
then we get
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$.
So, we have to prove the converse that if
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$,
then
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\order\tcztope{\ptemp}{\cen}{\sfact}$.

Let us consider
$\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}$.
Using
Lemma~\ref{lem:normalization}, we get
%
\begin{align*}
&
  \tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}=\cztope{\ptemp^\pr\diagonal{\sfact^\pr}}{\cen^\pr}\subseteq\tcztope{\ptemp}{\cen}{\sfact}\\ &\equivalent~\set{\cen^\pr+\ptemp^\pr\diagonal{\sfact^\pr}\zeta^\pr:~\zeta^\pr\in\compnums^m,~\infnorm{\zeta^\pr}\leq
    1}\subseteq\set{\cen+\ptemp\zeta:~\zeta\in\compnums^n,~\absolute{\zeta}\leq
    \sfact}\\ & \%\%~\text{since}~\ptemp~\text{is non-singular}\\ &
  \equivalent~
  \set{\inv{\ptemp}\lt(\cen-\cen\rt)+\inv{\ptemp}\ptemp^\pr\diagonal{\sfact^\pr}\zeta^\pr:~\zeta^\pr\in\compnums^m,~\infnorm{\zeta^\pr}\leq
    1}\\&\subseteq
  \set{\zeta:\zeta\in\compnums^n,~\absolute{\zeta}\leq\sfact}\\
 & \equivalent~\set{\inv{\ptemp}\ptemp^\pr\diagonal{\sfact^\pr}\zeta^\pr:~\zeta^\pr\in\compnums^m,~\infnorm{\zeta^\pr}\leq
    1}\subseteq
  \set{\zeta:\zeta\in\compnums^n,~\absolute{\zeta}\leq\sfact} ~\numberthis\label{proof-necc-inc1}
\end{align*}
%
Let $\tmat=\inv{\ptemp}\ptemp^\pr\diagonal{\sfact^\pr}$ and
$\tvect=0$.  Then by
Equation~\ref{proof-necc-inc1}, we get for any $i\in\set{1,...,n}$
%
\begin{align*}
\forall
& \max_{\zeta^\pr\in\compnums^m:~\infnorm{\zeta}}\tmat_i\zeta^\pr_i\leq
  1}\absolute{\sum_{i=1}^m\tmat_{ij}\zeta_i}\leq\sfact_i
& \implies \sum_{i=1}^n\tmat_i\frac{\absolute{\tmat_i}}{\tmat_i}
    \leq\sfact_i\\
    & \%\%~~\text{since}~y_i=0
& \implies \sum_{i=1}^n\absolute{\tmat_{ij}}  +\absolute{\tvect_i}\leq \sfact_i .~\numberthis\label{proof-necc-inc2}
\end{align*}
%
Furthermore, we have
%
\begin{align*}
&
  \ptemp\tmat=\ptemp\inv{\ptemp}\ptemp^\pr\diagonal{\sfact}=\ptemp^\pr\diagonal{\sfact^\pr}~\text{
    and }\\
& \ptemp\tvect=0=\cen-\cen.~\numberthis\label{proof-necc-inc3}      
\end{align*}
%
By Equations~\ref{proof-necc-inc2} and~\ref{proof-necc-inc4}, we get $\tcztope{\ptemp^\pr}{\cen}{\sfact^\pr}\order\tcztope{\ptemp}{\cen}{\sfact}$.
\end{proof}

