\section{Other Operations on Augmented Complex Zonotopes}
Earlier, we had discussed about the intersection of an augmented
complex zonotope with a suitably aligned sub-parallelotope.  We shall
now discuss about other operations on augmented complex zonotopes which
are linear transformation, Minkowski sum, projection along a direction
and checking inclusion.

Augmented complex zonotopes are closed under linear transformation and
Minkowski sum, which are described in the following two lemmas.
%
\begin{lemma}[Linear transformation]
Let us consider an augmented complex zonotope
$\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}\subset \compnums^n$
and a matrix $A\in\mat{n}{n}{\reals}$.  Then
%
\[
A\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}=\acztope{A\ptemp}{A\cen}{\sfact}{A\stemp}{\lb}{\ub}.
\]
%
\end{lemma}
%
\begin{proof}
{\color{red} TODO}.
\end{proof}
%
\begin{lemma}[Minkowski sum]
Let us consider two augmented complex zonotopes
$\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub},
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\subset\compnums^n$.
Then
%
\begin{align*}
& \minsum{\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}}
  {\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}}\\
& = \acztope
{\lt[\begin{matrix}
    \ptemp &
    \ptemp^\pr
  \end{matrix}\rt]
}
{\begin{matrix}
    \cen+\cen^\pr
  \end{matrix}
}
{\lt[\begin{matrix}
    \sfact\\
    \sfact^\pr
  \end{matrix}\rt]
}
{\lt[\begin{matrix}
    \stemp &
    \stemp^\pr
  \end{matrix}\rt]
}
{\lt[\begin{matrix}
    \lb\\
    \lb^\pr
  \end{matrix}\rt]
}
{\lt[\begin{matrix}
    \ub\\
    \ub^\pr
  \end{matrix}\rt]
}
\end{align*}
%
\end{lemma}
%
To problem of checking inclusion between two augmented complex
zonotopes can be equivalently expressed as the problem of checking
inclusion between two geometrically equivalent template complex
zonotopes.  For this, we propose the following conversion between the
real projection of an augmented complex zonotope and a template
complex zonotope.
%
\begin{lemma}
Let us consider an augmented complex zonotope
$\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}$.  Then we have the
following equivalence to the real projection of a template complex zonotope.
%
\begin{align*}
  \real\lt(\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}\rt)
  = \real\lt(\tcztope
  {\lt[\begin{matrix}
      \ptemp &
      \stemp
    \end{matrix}\rt]
  }
  {\begin{matrix}
      \cen+\frac{\ub+\lb}{2}
    \end{matrix}
  }
  {\lt[\begin{matrix}
      \sfact\\
      \frac{\ub-\lb}{2}
    \end{matrix}\rt]
  }
  \rt)
\end{align*}
%
\end{lemma}
%
So, to check inclusion between real projections of two augmented
complex zonotopes, we can equivalently check inclusion between the
real projections of corresponding template complex zonotopes.  In the
Definition~\ref{defn:inclusion-tcz} of the previous chapter, we had
proposed a relation $''\order''$, stated as a set of second order
conic program, for checking inclusion between two template complex
zonotopes.  Then based on the aforementioned equivalence between
augmented complex zonotopes and template complex zonotope, we extend
the inclusion checking relation to augmented complex zonotopes as
follows.
%
\begin{definition}[Relation between augmented complex zonotopes]
Given two augmented complex zonotopes $\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub},
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\subset\compnums^n$,
we say that
%
\[
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr} \order
 \acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}
\]
%
if and only if
%
\[
\real\lt(\tcztope
  {\lt[\begin{matrix}
      \ptemp^\pr &
      \stemp^\pr
    \end{matrix}\rt]
  }
  {\begin{matrix}
      \cen^\pr+\frac{\ub^\pr+\lb^\pr}{2}
    \end{matrix}
  }
  {\lt[\begin{matrix}
      \sfact^\pr\\
      \frac{\ub^\pr-\lb^\pr}{2}
    \end{matrix}\rt]
  }
  \rt)
  \order
  \real\lt(\tcztope
  {\lt[\begin{matrix}
      \ptemp &
      \stemp
    \end{matrix}\rt]
  }
  {\begin{matrix}
      \cen+\frac{\ub+\lb}{2}
    \end{matrix}
  }
  {\lt[\begin{matrix}
      \sfact\\
      \frac{\ub-\lb}{2}
    \end{matrix}\rt]
  }
  \rt).
\]
%
\end{definition}
%
\begin{theorem}[Inclusion checking]~\label{thm:acz-inclusion}
Let us consider two augmented complex zonotopes $\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub},
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\subset\compnums^n$.
Then the following inclusion
of the real projections is true
%
\[
\real\lt(\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\rt)\subseteq\real\lt(\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}\rt)
\]
%
if the following relation is true
%
\[
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\order\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}.
\]
%
\end{theorem}
%
\begin{proof}
  {\color{red} TODO}
\end{proof}
%
The following propostion states that the above sufficient condition
for checking the inclusion between the real projections of augmented
complex zonotopes is equivalently a second order conic constraint on a
variable of size proportional to the representation size of the
augmented complex zonnotopes.
%
\begin{proposition}
Let us consider two augmented complex zonotopes\\
$\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub},
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr}\subset\compnums^n$.
If $\ptemp$ and $\ptemp^\pr$ are considered constants, then the
relation
%
\[
\acztope{\ptemp^\pr}{\cen^\pr}{\sfact^\pr}{\stemp^\pr}{\lb^\pr}{\ub^\pr} \order
 \acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}
\]
%
is equivalent to a second order conic constraint on a variable of
length {\color{red} todo}, which comprises the primary offset $\cen$, scaling
factors $\sfact$ and lower and upper interval bounds $\lb$ and $\ub$,
respectively.
\end{proposition}
%
The support of an augmented complex zonotope along any direction is as
an affine function of the primary offset, scaling factors and the
upper and lower interval bounds.  This is described in the following
lemma.
%
\begin{lemma}[Linear projection]
Let us consider an augmented complex zonotope
$\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}$ and a vector
$v\in\compnums^n$.  Then
%
\begin{align*}
  & \support{w}{v}{\acztope{\ptemp}{\cen}{\sfact}{\stemp}{\lb}{\ub}}\\
  & = \mymatrix{\ptemp &
    \stemp}\lt(\cen+\frac{\ub+\lb}{2}-w\rt)+v^T\mymatrix{\ptemp & \stemp}\mymatrix{\sfact\\\frac{\ub-\lb}{2}}.
\end{align*}
%
\end{lemma}
%
\begin{proof}
{\color{red} todo}.
\end{proof}
%
