%
For any $\rho:0\leq \rho\leq \epsilon$, we want to derive a bound on the
contraction of the operator $H_{t+\rho}$ as a function of $H_t$ and
$\epsilon$.  Using Taylor expansion of an order $r$, we
can write
\begin{align*}
&
  H_{t+\rho}=e^{(A_c\rho)}H_t=P_r(\rho)H_t+E_r(\delta)H_t~~\text{where}\\
&  P_r(\rho)=\sum_{i=0}^r\frac{A_c^i\rho^i}{i!},~~~~~~
 E_r(\delta)=\frac{A_c^{r+1}\delta^{r+1}}{(r+1)!}:~~\delta\in[0,\epsilon].~\numberthis\label{eqn:taylor}
\end{align*}
%
To use the above expansion for deriving the bound on contraction, we
shall describe some properties of contraction.  The following
lemma states that the amount of contraction under transformation
by the product of two matrices is bounded by the product of amount of
contraction of individual matrices.  Also, the amount of contraction
under transformation by the sum of two matrices is bounded by the sum
of the amount of contraction of individual matrices.
%
\begin{lem}\label{lem:composition}
Let $J_1$ and $J_2$ be two linear operators and $\Psi$ be a $C$-set.
  Then the all of the following is true.
\begin{enumerate}
\item $\chi(\Psi,J_1+J_2)\leq\chi(\Psi,J_1)+\chi(\Psi,J_2)$.
\item $\chi(\Psi,J_1J_2)\leq\chi(\Psi,J_1)\chi(\Psi,J_2)$.
\end{enumerate}
\end{lem}
%
\begin{proof}
  For proving the first part, we derive the following.
  %
  \begin{align*}
&  \text{Since}\hspace{1em}   J_1\Psi\subseteq
    \chi(\Psi,J_1)\Psi~\text{ and }
    J_2\Psi\subseteq \chi(\Psi,J_2),~\text{we get}\\
&  (J_1+J_2)\Psi\subseteq
  \chi(\Psi,J_1)\Psi \oplus \chi(\Psi,J_2)\Psi=
  (\chi(\Psi,J_1) + \chi(\Psi,J_2))\Psi.
  \end{align*}
  %
For proving the second part, we derive the following.
\begin{align*}
  &  J_1J_2\Psi=J_1(J_2\Psi)\subseteq J_1(\chi(\Psi,J_2)\Psi)\\
 &=\chi(\Psi,J_2)\lt(J_1\Psi\rt)\subseteq
  \chi(\Psi,J_1)\chi(\Psi,J_2)\Psi.\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
If a matrix is embedded inside the convex hull of a set of matrices,
then we get the following bound on contraction by the matrix.
%
\begin{lemma}
Let us consider that $J\in\convexhull{\set{A_1,...,A_r}}$ and
$\Psi\subset\reals^n$.  Then
%
\begin{align*}
& \contraction{J}{\Psi}\leq\max_{i=1}^r\contraction{A_i}{\Psi}.
\end{align*}
%
\end{lemma}
%
\begin{proof}
As $J\in\convexhull{\set{A_1,...,A_r}}$, there exists
$\alpha_1,...,\alpha_r\in\reals_{\geq 0}$ such that
$\sum_{i=1}^r\alpha_i=1$ and $J=\sum_{i=1}^r\alpha_iA_i$.  Then by
using Lemma~\ref{lem:composition}, we get
%
\begin{align*}
  & \contraction{J}{\Psi}\leq\sum_{i=1}^r\contraction{A_i}{\Psi}\\
  & \leq \lt(\sum_{i=1}^r\alpha_i\rt)\max_{i=1}^r\contraction{A_i}{\Psi}=\max_{i=1}^r\contraction{A_i}{\Psi}.\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
\begin{lem}~\label{lem:convex}~\cite{todo}
Let us consider $\set{A_0,A_1,...,A_r}\subseteq\mat{n}{n}\reals$ such
that 
%
\[
\forall j\in\{0,...,r\},~ U_j(\rho)=\sum_{i=0}^jA_i\rho^i.
\]
%
If
$0\leq\rho\leq \epsilon$, then $U_r(\rho)\in
\convexhull{U_0(\epsilon),U_1(\epsilon),...,U_r(\epsilon)}$.
\end{lem}
\begin{proof}
This has been proved in~\cite{todo}.
\end{proof}

Using the above results, we derive the following bound on contraction
by the operator $H_{t+\rho}$, when $\rho\in[0,\epsilon]$.
%
\begin{lemma}\label{lem:conv}
Let us consider $\Psi\subset\reals^n$ and $\rho\in[0,\epsilon]$.  If
$0\leq \rho\leq \epsilon$, then
%
\begin{align*}
& \contraction{H_{t+\rho}}{\Psi}\leq\max_{i=1}^r\contraction{P_r(\epsilon)H_t}{\Psi}+\contraction{\frac{A_c^{r+1}}{(r+1)!}H_t}{\Psi}\epsilon^{r+1}.
\end{align*}
%
\end{lemma}
%
\begin{proof}
Using Equation~\ref{eqn:taylor}, there exists
$\delta\in[0,\epsilon]$ such that,
%
\begin{align*}
&
  \contraction{H_{t+\rho}}{\Psi}=\contraction{P_r(\rho)+E_r(\delta)}{\Psi}\\
& \%\%~~\text{by Lemma~\ref{lem:composition}}\\
&
  \leq\contraction{P_r(\rho)H_t,\Psi}+\contraction{\frac{A_c^{r+1}}{(r+1)!}H_t}{\Psi}\delta^{r+1}\\
  & \%\%~~\text{by Lemma~\ref{lem:convex}}\\
&
  \leq\max_{i=1}^r\contraction{P_r(\epsilon)H_t}{\Psi}+\contraction{\frac{A_c^{r+1}}{(r+1)!}H_t}{\Psi}\delta^{r+1}\\
& \leq\max_{i=1}^r\contraction{P_r(\epsilon)H_t}{\Psi}+\contraction{\frac{A_c^{r+1}}{(r+1)!}H_t}{\Psi}\epsilon^{r+1}.\hspace{3em}\qedhere
\end{align*}
%
\end{proof}
%
As $P_r(\epsilon)$ is a function of $H_t$ and 
